\chapter{Introduction}
\section{Act-R}


ACT-R, acronym of Adaptive Control of Thought-Rational, is a cognitive architecture: a theory about how human cognition works. 
The aim of\mbox{ACT-R} is to model the behaviour of the human brain. From an external point of view\mbox{ACT-R} can be intended as a programming language; however its internal structure is based on assumptions about human cognition. The assumptions are established by psychologists, who research and study the human cognition, through numerous experiments ~\cite{Allen94}. 

A feature that distinguishes\mbox{ACT-R} from other theories in the field relies in allowing researchers to collect quantitative measures that can be directly compared with the quantitative measures obtained from human participants. These measures are compared between humans and\mbox{ACT-R}, they are the traditional one of cognitive psychology: time needed to perform the task, accuracy in the task and neurological data. For each task the researchers write programs in\mbox{ACT-R}, called models, adding their own assumptions related to the task. A model simulates the behaviour of a cognitive agent. The approach based on measuring and comparison leads to very effective models, in example it had been shown that\mbox{ACT-R} can successfully predict \emph{Blood-Oxygen-Level Dependence (BOLD)} of several parts of the brain, through experiments with \emph{Functional Magnetic Resonance Imaging (fMRI)}.
Up to now\mbox{ACT-R} has been used successfully to create models in many different areas, the most important of witch are: learning, problem solving, communication and perception.

ACT-R's most important assumption is that human knowledge can be divided into two irreducible kinds of representations: declarative and procedural.
Declarative memory refers to all the kind of memory that can be consciously recalled, like the shape of an object or its color. Procedural memory is, instead, very different from the declarative one: it is referred to actions that can be done unconsciously. The most common way, used to explain how these two kind of memory work, is the typewriter example.
A skilled typewriter can write quickly without looking at the keyboard, he just puts his fingers in the right place and push the right keys, in the correct order. If we ask to the same typewriter where a certain character is positioned in his keyboard, he will probably answer that he's not sure about that without looking at it, even if he writes the whole day. In this example the procedural memory is stored as the action of putting the right finger in the right place when the typewriter has the goal to write a certain character.

In\mbox{ACT-R} theory the declarative memory is represented by the so called \emph{chunks}, data structures defined as a n-tuple (slots) of arbitrary size. The n-tuples and their values are specified in the \emph{chunk-type}, it defines also (if any) the initial value of the slot. Every chunk has also a name, used to reference it, but that is not considered to be a part of the chunk itself. The chunks and their slots are used to implement the mechanisms of\mbox{ACT-R} theory, even if the slots are only software construct and not part of the theory itself. The chunk-types can be organized in hierarchy.

The\mbox{ACT-R} counter part of the human procedural memory are the \emph{productions}. Productions are the\mbox{ACT-R} equivalent of functions, they define sequences of actions and can be fired only if a set of preconditions are satisfied. 

Both the declarative memory and the procedural memory are called \emph{modules} of \mbox{ACT-R}.  The many activities carried out by the brain, i.e. talking or moving, are performed by neurons located together, in the same areas. In analogue way each module of\mbox{ACT-R} represents a function of the human brain. In all this infrastructure the task of the procedural module is to coordinate all the other modules. The exchange of information between the modules is achieved through \emph{buffers}.

The buffers are the built in interface between modules. Every buffer is connected to a module, while a module can also have no buffers. The role of the modules is to relay queries for actions from the module and to get information about the internal state of the module. Each module can hold maximum one chunk, accessible in read only from all the other module, and in read and write mode for the module owner of the buffer. The modules usually work in a parallel way, but their interaction is only serial. There are two reasons for this kind of interaction: the first one is due to the structure of the buffers, that can hold only one chunk at a certain time; the second one is to allow only one production, which have its preconditions satisfied, to be fired.


ACT-R is the ultimate successor of a series of increasingly precise models of human cognition, developed by John R. Anderson. Anderson credits Allen Newell as source of influence to his theory.


As programming language,\mbox{ACT-R} is a framework: it provides generic features and functionality, that can be specialized for different task. In\mbox{ACT-R} for different tasks 
(e.g., Tower of Hanoi, memory for text or for list of words, language comprehension, 
communication, aircraft controlling), researchers create "models" (i.e., programs) in\mbox{ACT-R}. 
These models reflect the modelers' assumptions about the task within the\mbox{ACT-R} view of 
cognition.
\section{OpenCV}
\section{The objective}